Geographical Python Teaching Resources: GeoPyTeR

### 2020-02-26 Geopyter.tex
Added useful OER links.

\comment{Work in OER material below}

Going back to the drawing board, we looked again at our own experiences of successful programming and instructional efforts. In particular, we took note of two powerful streams of thought in software and education: the importance attached by the Free and Open Source Software (\textsc{foss}) movement to both peer-recognition \citep{raymond_cathedral_1999} and distributed version control; and the rise of Virtual Learning Environments (\textsc{vle}s) and of Massive Open Online Courses (\textsc{mooc}s) with their use of rich, online learning experiences (\eg \citealp{Trafford2011,Cabiria2012}). Reflecting on our initial failure, we decided against trying to supply a single set of polished course materials and instead looked for a way to provide teachers with building blocks from which they could assemble an \emph{individualised} course suited to their institutional and pedagogical needs.

@@

@@

\comment{Convert into a Jupyter-like example.}

>>>>

Going back to the drawing board, we looked again at our own experiences of successful programming and instructional efforts. In particular, we took note of two powerful streams of thought in software and education with which we already familiar: the importance attached by the Free and Open Source Software (\textsc{foss}) movement to both peer-recognition \citep{raymond_cathedral_1999} and distributed control; and the rise of Virtual Learning Environments (\textsc{vle}s) and Massive Open Online Courses (\textsc{mooc}s) with their use of rich, online learning experiences (\eg \citealp{Trafford2011,Cabiria2012}). Reflecting on our initial failure, we decided against trying to supply a single set of polished course materials and instead looked for a way to provide teachers with building blocks from which they could assemble an \emph{individualised} course suited to their institutional and pedagogical needs.

@@

Without realising it, we were plugging into a larger framework of thinking emerging from the literature on Open Educational Resources (\textsc{oer}), which began as largely `legal and economic concept' designed to support royalty and license free access to educational resources \citep{butcher2010open}. It should be clear from this definition that there is no \emph{necessary} link to \textsc{foss} since a free e-book can qualify as an \textsc{oer}. However, these two areas are conceptually aligned in many ways, not least through their shared interest in the `4 Rs': reuse, redistribution, revision, and remixing \citep{Hilton2010}. Within \citeauthor{du2017}'s \citeyearpar{du2017} \textsc{oer} typology \gp is clearly `open courseware', but it is conceptually distinct from \textsc{mit}'s eponymous OpenCourseWare or Standford's Coursera since it is designed to promote what \citeauthor{Ehlers2011} calls `Open Educational Practice' \citeyearpar{Ehlers2011} in a manner not altogether dissimilar to that the Geographic Science \& Technology Body of Knowledge \citep{bok2018}.

In line with \citet{Mishra2017} and with \citeauthor{Knox2013}'s \citeyearpar{Knox2013} call for a role for pedagogy in \textsc{oer}, \gp envisions an essential role for `teachers as (co)creators': they not only have an active role in selecting components for a Session or Module, they can contribute source material as well. The educator and section editors, of which more later, may therefore also use this process to extend their own understanding in an applied workplace setting through collaboration (see \citealp{littlejohn2017} and \citealp{eraut2008} for relevant discussions). Of course, we must also recognise that under \citeauthor{Wiley2009}'s \citeyearpar{Wiley2009} \textsc{alms} typology, although \gp provides direct Access to editing tools, is Meaningfully editable, and offers Source-file access, the Level of expertise required is not insubstantial though we also expect instructors in this domain to be more comfortable than most with the process. We therefore believe that \gp is unique in incorporating the instructor's domain expertise and pedagogical strategies by design.

@@
